---
title: "class13 Structural Bioinformatics"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## get HIV-Pr structure from PDB Database

We will work with the structure `1HSG` 
```{r cars}
library(bio3d)

file.name <- get.pdb("1HSG")
```

Read this into R and examine composition
```{r}
hiv <- read.pdb(file.name)

hiv
```

## Slit into separate protein and ligand files

We will use the `trim.pdb()` function to split our input structure
```{r}
prot <- trim.pdb(hiv, "protein")
prot

lig <-trim.pdb(hiv, "ligand")
lig
```

We will use the `write.pdb()` function to write our structures
```{r}
write.pdb(prot, file="1hsg_protein.pdb")
write.pdb(lig, file="1hsg_ligand.pdb")
```

## Inspecting our docking results with Vina

We run this command:
`~/Downloads/autodock_vina_1_1_2_mac/bin/vina --config config.txt --log log.txt

We got a file `all.pdbqt` that we need to made into a PDB format
```{r}
res <- read.pdb("all.pdbqt", multi=TRUE)

res

write.pdb(res, "results.pdb")

```

We will use the `rmsd()` function to compare our docking results
```{r}
ori <- read.pdb("ligand.pdbqt")

rmsd(ori, res)
```

## Normal mode analysis

Normal mode analysis (NMA) is one of the major simulation techniques used to probe large- scale motions in biomolecules. Typical application is for the prediction of functional motions in proteins.
Normal mode analysis (NMA) of a single protein structure can be carried out by providing a PDB object to the function `nma()`. In the code below we first load the Bio3D package and then download an example structure of hen egg white lysozyme (PDB id 1HEL) with the function `read.pdb()`. Finally the function `nma()` is used perform the normal mode calculation:
```{r}
pdb <- read.pdb("1HEL")

modes <- nma(pdb)

plot(modes, sse=pdb)

#visualize NMA results
mktrj(modes, mode=7, file="nma_7.pdb")
```

